Library Learning in Neurally-Guided Bayesian Program Induction

### 2018-10-26 nips_2018.tex
more related work

 \noindent \textbf{Inventing new subroutines for program induction:}
 Several program induction algorithms, most prominently the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}, take as their goal to learn new, reusable subroutines that are shared in a multitask setting. We find this work inspiring and motivating,
 and extend it along two dimensions: (1) we propose a new algorithm for
 inducing reusable subroutines, based on Fragment Grammars~\cite{tim};
 and (2) we show how to combine these techniques with bottom-up neural recognition models.
 Other instances of this related idea are~\cite{DBLP:conf/icml/LiangJK10}, Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}, MagicHaskeller~\cite{katayama2015towards}, Bayesian program merging~\cite{hwang2011inducing}, and predicate invention in Inductive Logic Programming~\cite{DBLP:conf/ecai/LinDETM14}.

@@

 We have presented an algorithm that, starting from relatively little,
 learned to solve nontrivial program synthesis problems in three
 different domains.  However, our system was also given (and also,
 critically \emph{needs}) a corpus of training tasks to solve for each
 domain.  Is constructing (or curating) corpra of tasks any easier or
 better than hand-engineering DSLs?  In the immediate future, we
 expect some degree of hand-engineering of DSLs to continue, especially
 in domains where humans have strong intuitions about the underlying
 system of domain specific concepts, like text editing. However, if
 program induction is to become a standard part of the AI toolkit,
 then, in the long-term, we need to build agents that autonomously
 acquire the domain specific knowledge needed to navigate a new
 domain.  So, through the lens of program synthesis, EC$^2$ carries
 the limitation that it requires a high-quality corpus of training
 tasks; but, for the program-induction approach to AI, this limitation
 is natural.

>>>>

 \noindent \textbf{Inventing new subroutines for program induction:}
 Several program induction algorithms, most prominently the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}, take as their goal to learn new, reusable subroutines that are shared in a multitask setting. We find this work inspiring and motivating,
 and extend it along two dimensions: (1) we propose a new algorithm for
 inducing reusable subroutines, based on Fragment Grammars~\cite{tim};
 and (2) we show how to combine these techniques with bottom-up neural recognition models.
 Other instances of this related idea are~\cite{DBLP:conf/icml/LiangJK10}, Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}, MagicHaskeller~\cite{katayama2015towards}, Bayesian program merging~\cite{hwang2011inducing}, and predicate invention in Inductive Logic Programming~\cite{DBLP:conf/ecai/LinDETM14}.
 Concurrent with this work, closely related ideas were applied to mining `code idioms' from imperative programs~\cite{8355713}
 and for synthesizing functional programs from natural language~\cite{Alex}.

@@

 We have presented an algorithm that, starting from relatively little,
 learned to solve program synthesis problems in three
 different domains.  However, our system was also given (and also,
 critically \emph{needs}) a corpus of training tasks to solve for each
 domain.  Is constructing (or curating) corpra of tasks any easier or
 better than hand-engineering DSLs?  In the immediate future, we
 expect some degree of hand-engineering of DSLs to continue, especially
 in domains where humans have strong intuitions about the underlying
 system of domain specific concepts, like text editing. However, if
 program induction is to become a standard part of the AI toolkit,
 then, in the long-term, we need to build agents that autonomously
 acquire the domain specific knowledge needed to navigate a new
 domain.  So, through the lens of program synthesis, EC$^2$ carries
 the limitation that it requires a high-quality corpus of training
 tasks; but, for the program-induction approach to AI, this limitation
 is natural.
